\begin{abstract}  
	% The abstract is summary of the work with emphasis on the findings of the study. It is not intended to be an {\em introduction} to the research. Instead, it should concisely state the problem addressed, the methods developed and used, and the results obtained. It must be single spaced and no more than one page in length. It must use the same font and font size as the rest of the work. The abstract precedes the acknowledgment page and the body of the work.
	This thesis explores the use of software-defined radios (SDRs) to develop a low-cost radar
	system for avalanche detection.
	Avalanches are a significant danger in mountainous locations and existing systems are
	often difficult or expensive to use.
	This research asseses if commercially available SDRs can be used to create a radar
	system capable of detecting moving targets and accurately measuring distance.


	A frequency-modulated contiuous-wave (FMCW) radar was implemented using the LimeSDR-Mini
	and the USRP B210. Signal generation, data collection, and processing all are performed
	in software, enabling easy configuration. Improvements to data transfer methods
	for the LimeSDR-Mini reduced sampling errors and improved system performance.
	Testing with the USRP B210 demonstrated successful detection of moving targets,
	including a corner reflector up to 80 meters and large objects up to 155 meters.


	Results show that SDR-based radar systems are a practical and low-cost option
	for avalanche detection, however, further improvements in hardware, interferance
	reduction, and field testing are required before deployment.
\end{abstract}